\chapter{Introduction}
\label{cha:introduction}

\section{Chair's message}
\label{sec:chairs-message}

Welcome to the Department of Electrical and Computer Engineering at Weber State University! As a student in our Electrical and Computer Engineering (ECE) program, you are embarking on an exciting journey of discovery, innovation, and personal growth. This handbook is designed to provide you with essential information about the program’s curriculum, academic policies, resources, and opportunities available to you during your undergraduate studies. We encourage you to familiarize yourself with the contents of this handbook and refer to it whenever you have questions about your academic journey.

\section{About ECE}
\label{sec:about-departm-electr}

The Department of Electrical and Computer Engineering at Weber State University is committed to providing high-quality education and fostering a supportive learning environment for aspiring electrical and computer engineers. Our distinguished faculty members are experts in various fields of electrical and computer engineering, and they are dedicated to helping you succeed academically and professionally. Our state-of-the-art laboratories, cutting-edge research initiatives, and collaborative learning opportunities ensure that you receive a well-rounded education and are prepared to tackle the challenges of the modern world.

In this handbook, you will find detailed information about the ECE program's curriculum, academic policies, available resources, and the various opportunities that will enhance your learning experience. We encourage you to take full advantage of the resources and support services offered by the department to make the most of your time here.

We wish you a fulfilling and successful academic journey in the Department of Electrical and Computer Engineering at Weber State.

%%% local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
