
\chapter{Department Organization}
\label{cha:departm-organ}

\section{Department structure}
\label{sec:department-structure}

The Electrical and Computer Engineering Department is structured to provide students with a robust academic foundation and real-world applications. The department is led by a dedicated team of experienced faculty members and administrators who are passionate about advancing the field of electrical and computer engineering.
\begin{flushleft}
\begin{tabular}{p{8cm}p{6cm}}
\textbf{Position} & \textbf{Name} \\
Chair & Fon Brown, PhD \\
Undergraduate Program Coordinator & Eric Gibbons, PhD \\
Graduate Program Director & Jutin Jackson, PhD \\
\end{tabular}
\end{flushleft}

The ECE faculty members are experts in various fields, including electronics, communications, computer systems, robotics, and power systems. Students are encouraged to interact with faculty members, attend their office hours, and seek mentorship for academic and research pursuits.

\subsection{ECE Advising and Support}
\label{sec:ece-faculty-direct}


In addition to faculty members, the department has dedicated staff members who assist with administrative, advising, and technical support services. The staff directory provides contact information for administrative assistants, advisors, laboratory technicians, and other support personnel.

\begin{flushleft}
\begin{tabular}{p{8cm}p{6cm}}
\textbf{Position} & \textbf{Name} \\
Administrative assistant & Judy Smith \\
Academic advisor & Aimee Smith \\
Graduate enrollment director & Rainie Ingram \\
\end{tabular}
\end{flushleft}


\subsection{Office hours and contact information}
\label{sec:office-hours-contact}

Faculty and staff members have designated office hours during which students can ask questions, seek clarification, and discuss academic matters. Office hours are posted on the department's website and outside individual faculty offices. Contact information for faculty and staff members is also available online.


\section{Department facilities}
\label{sec:departm-facil}

Our department boasts state-of-the-art laboratories equipped with the latest technology.


providing students with hands-on experience in areas such as:

Digital Signal Processing
Robotics and Automation
Integrated Circuit Design
Power Systems
Wireless Communication


\section{Student resources}
\label{sec:student-resources}

\subsection{Academic advising}
\label{sec:academic-advising}


Our dedicated academic advisors assist students in course selection, career planning, and graduate school applications. Regular advising sessions ensure that students stay on track to meet their academic and career goals.

\subsection{Career services}
\label{sec:career-services}

The ECE Department collaborates with the college's Career Services center to provide internship and job placement opportunities, career fairs, and networking events with industry professionals. Workshops on resume building and interview skills are also offered.

\subsection{Student clubs and organizations}
\label{sec:stud-clubs-organ}

Engage with like-minded peers and enhance your leadership skills by joining student organizations such as the IEEE Student Branch and Tau Beta Pi. These organizations offer a platform to collaborate on projects, attend conferences, and participate in competitions, enriching your overall university experience.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
